%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Edstem.py} $|$ \emph{Python, asyncio, aiohttp, websockets} $|$ github.com/bachtran02/edpy}{}
    \resumeItemListStart
        \resumeItem{
        Designed and implemented a client library for EdSTEM, an educational Q\&A platform with 1M+ users, enabling third-party platforms to ingest real-time course and thread activity.
        }
        \resumeItem{
       Reverse-engineered EdSTEM’s internal pub/sub system to decode undocumented WebSocket events and extract low-level payloads for custom API methods.
        }
        \resumeItem{
       Deployed a Python webhook service that streams Ed post notifications to Discord platform, achieving 99\% uptime.}

    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{GradescopeSync} $|$ \emph{Python, Beautiful Soup, GitHub Actions} $|$ github.com/bachtran02/GradescopeSync}{}
    \resumeItemListStart        
        % \resumeItem{
        % Developed a modular Python scraper leveraging Beautiful Soup to programmatically extract and structure assignment metadata from Gradescope's authenticated interface.
        % }
        % \resumeItem{
        % Automated the syncing of Gradescope assignment deadlines with Google Tasks to support efficient task tracking.
        %  }
        % \resumeItem{
        % Orchestrated a CI-based scheduling system with GitHub Actions to dispatch daily assignment summaries via text platforms, ensuring timely reminders without user intervention.
        % }
        \resumeItem{
        Engineered a web scraper to extract structured assignment data from Gradescope’s authenticated interface, improving deadline visibility and task organization for STEM students.
        }
        \resumeItem{
        Orchestrated a CI-based scheduler with GitHub Actions to automate daily SMS delivery of assignment summaries, maintaining 99\% reliability without manual input.
        }
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Pintos Operating System} $|$ \emph{C, GDB, x86 architecture} }{}
    \resumeItemListStart
        \resumeItem{
        Implemented system call handlers bridging user programs and kernel, supporting core process life-cycle operations including creation, termination, and context switching.
        }
        \resumeItem{
        Enabled multi-threading on a single-core system by implementing thread management syscalls, priority-based scheduling, and synchronization primitives (locks, semaphores, condition variables).
        }
        \resumeItem{
        Enhanced the file system to support dynamic file growth via non-contiguous block allocation and a buffer cache with a clock-based eviction strategy, optimizing disk utilization and I/O performance.
        }
        
    \resumeItemListEnd
    

\resumeSubHeadingListEnd